Missing the Point\(\colon\) Non-Convergence in Iterative Imputation Procedures

### 2020-04-10 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Wrote new autocorrelation function instead :)
Removed old plots, now all with missingness percentages

```{r, include = FALSE}
load("../Results/combined.Rdata")
source("../2.CreateFigures.R")
```

```{r}
bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of means, 75% missingness")
```

```{r}
bias_sds_plot + R_sds_plot + AC_sds_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of variances, 75% missingness")
```

```{r}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of effects, 75% missingness")
```

@@

dat %>% ggplot(aes(x = T, y = bias.R.s, color = miss)) + 
  geom_point() +
  geom_line() +
  ylab(expression(paste("Bias in ", hat(R ^ 2)))) +
  labs(colour = "Legend: missingness percentage") +
  plot_annotation(title = "The effect of missingness percentage, an example")

>>>>

```{r, include = FALSE}
load("../Results/complete.Rdata")
source("../2.CreateFigures.R")
```

<!-- ```{r} -->
<!-- bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of means, 75% missingness") -->
<!-- ``` -->

@@

dat %>% ggplot(aes(x = T, y = bias.R.s, color = as.factor(miss))) + 
  geom_point() +
  geom_line() +
  ylab(expression(paste("Bias in ", hat(R ^ 2)))) +
  labs(colour = "Legend: missingness percentage") +
  plot_annotation(title = "The effect of missingness percentage, an example")

### 2020-04-10 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Wrote new autocorrelation function instead :)
Removed old plots, now all with missingness percentages

@@

\textbf{Add the function \texttt{mvtnorm::rmvnorm()} back in}

@@

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-4-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-5-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-6-1} \end{flushleft}

>>>>

\textbf{Add: missingness percentage = proportion of cases with one or
more missing values times 100 }

@@

\textbf{Add the function \texttt{mvtnorm::rmvnorm()} back in} use
citation(``mvtnorm'')

@@
